---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ruin

[![Travis-CI Build Status](https://travis-ci.org/irudnyts/ruin.svg?branch=master)](https://travis-ci.org/irudnyts/ruin)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/irudnyts/ruin?branch=master&svg=true)](https://ci.appveyor.com/project/irudnyts/ruin)

## Overview

The intention of the package is to provide simulation methods of common risk processes in a framework of ruin theory. Each model is implemented as an S4 class, having a simulator of its path, and a plotting function. Further, a Monte-Carlo estimator of a ruin probability for a finite time is implemented, using a parallel computation. Currently, the package extends two classical risk models, namely, Cramer-Lundberg and Sparre Andersen models by including capital injections (positive jumps).

## Installation

The package is not yet submitted to CRAN. Instead, you can install `ruin` from
github with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("irudnyts/ruin")
```

## Example

```{r example}
library(ruin)

model <- CramerLundberg(
  initial_capital = 10,
  premium_rate = 1,
  claim_poisson_arrival_rate = 1,
  claim_size_generator = rexp,
  claim_size_parameters = list(rate = 1)
)

ruin_probability(model = model, time_horizon = 10, return_paths = FALSE)
```
